\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2025-05-30 manuscript/manuscript.tex

@@

\section{Appendix}\label{sec:appendix}
In our original setting, we used a block size of $l = \lceil n^{1/3} \rceil$.
However, the optimal block size may vary according to the dependence structure.
To address this, we considered  using the automatic block-length selection
scheme
for
circular block bootstrap as described in Section 3.3 of
\citet{politis2004automatic}. Unfortunately, using this setting results in
the selection of
block
sizes that can be quite large (sometimes as large or larger than $n$), leading
to less variation between the bootstrapped
samples. Figures~\ref{fig:large_block} and \ref{fig:large_block}
demonstrate that for highly temporally
dependent samples (especially when the autocorrelation is negative),
the block size is frequently larger than $\sqrt{n}$.

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/large_block}
  \caption{Proportion of selected block sizes using
  \citet{politis2004automatic}'s procedure that are larger than the sample size
    $n$ for $n \in \{100, 200, 400, 800\}$,
    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
    $N(8,8)$ and $\Gamma(8,1)$.
  }
  \label{fig:large_block}
\end{figure}

@@

@@

Despite this, our 
algorithm holds its size somewhat well for moderately dependent
series as demonstrated in 
Figures~\ref{fig:alt_normal} and \ref{fig:alt_gamma}. Both 
\citet{politis2004automatic}'s setting and the cubic root setting result
in the method not holding its size for $|\tau| > 0.5$. 
Figure~\ref{fig:alt_rr} also shows that the two setting are comparably
powerful for $|\tau| <= 0.5$. However, we still
recommend the cubic root setting over that introduced by 
\citet{politis2004automatic} because the latter fails to hold its size
for negative $\tau$, particularly for smaller sample sizes. It is important to 
note that another block size selection rationale could yield better results.

@@

\item[Data availability statement:] The data and code used in the real data analysis and simulation studies are publicly available in a GitHub repo:

\url{https://github.com/mathewchandy03/Bootstrap_KS_Test}.

>>>>

\newcommand{\jy}[1]{\textcolor{red}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{blue}{(EDS: #1)}}
\newcommand{\mc}[1]{\textcolor{green}{(MC: #1)}}
\newcommand{\xz}[1]{\textcolor{cyan}{(XZ: #1)}}

@@

\appendix

\section{Block Size Investigation}\label{sec:appendix}

In our original setting, we used a block size of $l = \lceil n^{1/3} \rceil$.
However, the optimal block size may vary according to the dependence structure.
To address this, we considered  using the automatic block-length selection
scheme
for
circular block bootstrap as described in Section 3.3 of
\citet{politis2004automatic}. Unfortunately, using this setting results in
the selection of block
sizes that can be quite large (sometimes as large or larger than $n$), leading
to less variation between the bootstrapped
samples. Figures~\ref{fig:large_block}
demonstrate that for highly temporally
dependent samples (especially when the autocorrelation is negative),
the block size is frequently larger than $\sqrt{n}$.

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/large_block}
  \caption{Proportion of selected block sizes using the method of
  \citet{politis2004automatic} that are larger than the sample size
    $n$ for $n \in \{100, 200, 400, 800\}$,
    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
    $N(8,8)$ and $\Gamma(8,1)$.
  }
  \label{fig:large_block}
\end{figure}

@@

\jy{How do you interpret the flat lines in the plot? Why are the
  empirical cdf step functions? That means your empirical p-values are
  discrete with point masses at a few points. Check the p-values from
  the simulations.}
\mc{this was a result of erroneous data, it is fixed now}

@@

Despite this, our 
algorithm holds its size somewhat well for moderately dependent
series as demonstrated in 
Figures~\ref{fig:alt_normal} and \ref{fig:alt_gamma}. Both 
\citet{politis2004automatic}'s setting and the cubic root setting result
in the method not holding its size for $|\tau| > 0.5$. 
Figure~\ref{fig:alt_rr} also shows that the two settings are comparably
powerful for $|\tau| <= 0.5$. However, we still
recommend the cubic root setting over that introduced by 
\citet{politis2004automatic} because the latter fails to hold its size
for negative $\tau$, particularly for smaller sample sizes. It is important to 
note that another block size selection rationale could yield better results.

@@

\item[Data availability statement:] The data and code used in the real data analysis and simulation
studies are publicly available in a GitHub repo:\\
\url{https://github.com/mathewchandy03/Bootstrap_KS_Test}.
